Chemical tagging can work: \\ Identification of stellar phase-space structures \\ purely by chemical-abundance similarity\vspace{-7ex}

### 2016-08-13 papers/kmeans/kmeans.tex
final tweaks

\title{Chemical tagging can work: \\
       Identification of stellar phase-space structures \\
       purely by chemical-abundance similarity\vspace{-7ex}}
\author{David~W.~Hogg\altaffilmark{1,2,3,4},
        Andrew~R.~Casey\altaffilmark{5},
        Melissa~Ness\altaffilmark{4},
        Hans-Walter~Rix\altaffilmark{4},
        Daniel~Foreman-Mackey\altaffilmark{6,7},
        Sten~Hasselquist\altaffilmark{8,9},
        Anna~Y.~Q.~Ho\altaffilmark{10},
        Jon~A.~Holtzman\altaffilmark{8},
        Steven~R.~Majewski\altaffilmark{9},
        Sarah~L.~Martell\altaffilmark{11},
        Szabolcs~M\'esz\'aros\altaffilmark{12},
        David~L.~Nidever\altaffilmark{13},
        Matthew~Shetrone\altaffilmark{14}}
\altaffiltext{1}{Simons Center for Data Analysis, 160 Fifth Avenue, 7th floor, New York, NY 10010, USA}
\altaffiltext{2}{Center for Cosmology and Particle Physics, Department of Physics,
  New York University, 4 Washington Pl., room 424, New York, NY 10003, USA}
\altaffiltext{3}{Center for Data Science, New York University, 726 Broadway, 7th floor, New York, NY 10003, USA}
\altaffiltext{4}{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117 Heidelberg, Germany}
\altaffiltext{5}{Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3~0HA, UK}
\altaffiltext{6}{Sagan Fellow}
\altaffiltext{7}{Department of Astronomy, University of Washington, Box 351580, Seattle, WA 98195, USA}
\altaffiltext{8}{New Mexico State University, Las Cruces, NM 88003, USA}
\altaffiltext{9}{Department of Astronomy, University of Virginia, Charlottesville, VA 22904-4325, USA}
\altaffiltext{10}{Astronomy Department, California Institute of Technology, MC 249-17, 1200 East California Blvd, Pasadena, CA 91125, USA}
\altaffiltext{11}{School of Physics, University of South Wales, Sydney 2052, Australia}
\altaffiltext{12}{ELTE Gothard Astrophysical Observatory, H-9704 Szombathely, Szent Imre Herceg st. 112, Hungary}
\altaffiltext{13}{Steward Observatory, 933 North Cherry Ave, Tuscon, AZ 85719, USA}
\altaffiltext{14}{University of Texas at Austin, McDonald Observatory, USA}

>>>>

\title{Chemical tagging can work: \\
       Identification of stellar phase-space structures \\
       purely by chemical-abundance similarity\vspace{-7ex}}
\author{David~W.~Hogg\altaffilmark{1,2,3,4},
        Andrew~R.~Casey\altaffilmark{5},
        Melissa~Ness\altaffilmark{4},
        Hans-Walter~Rix\altaffilmark{4},
        Daniel~Foreman-Mackey\altaffilmark{6,7},
        Sten~Hasselquist\altaffilmark{8},
        Anna~Y.~Q.~Ho\altaffilmark{9},
        Jon~A.~Holtzman\altaffilmark{8},
        Steven~R.~Majewski\altaffilmark{10},
        Sarah~L.~Martell\altaffilmark{11},
        Szabolcs~M\'esz\'aros\altaffilmark{12},
        David~L.~Nidever\altaffilmark{13},
        Matthew~Shetrone\altaffilmark{14}}
\altaffiltext{1}{Simons Center for Data Analysis, 160 Fifth Avenue, 7th floor, New York, NY 10010, USA}
\altaffiltext{2}{Center for Cosmology and Particle Physics, Department of Physics,
  New York University, 4 Washington Pl., room 424, New York, NY 10003, USA}
\altaffiltext{3}{Center for Data Science, New York University, 726 Broadway, 7th floor, New York, NY 10003, USA}
\altaffiltext{4}{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117 Heidelberg, Germany}
\altaffiltext{5}{Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3~0HA, UK}
\altaffiltext{6}{Sagan Fellow}
\altaffiltext{7}{Department of Astronomy, University of Washington, Box 351580, Seattle, WA 98195, USA}
\altaffiltext{8}{New Mexico State University, Las Cruces, NM 88003, USA}
\altaffiltext{9}{Astronomy Department, California Institute of Technology, MC 249-17, 1200 East California Blvd, Pasadena, CA 91125, USA}
\altaffiltext{10}{Department of Astronomy, University of Virginia, Charlottesville, VA 22904-4325, USA}
\altaffiltext{11}{School of Physics, University of New South Wales, Sydney 2052, Australia}
\altaffiltext{12}{ELTE Gothard Astrophysical Observatory, H-9704 Szombathely, Szent Imre Herceg st. 112, Hungary}
\altaffiltext{13}{Steward Observatory, 933 North Cherry Ave, Tuscon, AZ 85719, USA}
\altaffiltext{14}{University of Texas at Austin, McDonald Observatory, USA}
